---
title: "hw_21_10"
author: "lnguen_1, Нгуен Лонг Зюи БЭК 171, группа 4"
date: "8/10/2018"
output: html_document
---




Install packages and download data:
```{r}
library(dplyr)
library(ggplot2)
library(readr)

airline = read_csv("~/shared/minor2_2018/1-intro/data/airline_sub_4.csv")
airport = read_csv("~/shared/minor2_2018/1-intro/data/airport_sub_4.csv")
lounge = read_csv("~/shared/minor2_2018/1-intro/data/lounge_sub_4.csv")
seat = read_csv("~/shared/minor2_2018/1-intro/data/seat_sub_4.csv")
```

# 1. First, we will look at the airline's data, I predict that overall_rating is proportional to the recommended rate of customer feedback.
```{r}
#I created a new data frame includes variables : airline_recommended, airline_rating, airline_recommended, airline_rating, count_feedback, ratio_recommended
airline_properties = airline%>%filter(is.na(overall_rating)==FALSE)%>%group_by(airline_name)%>%summarise(airline_recommended = sum(recommended), airline_rating = mean(overall_rating, na.rm = TRUE), count_feedback = n(), ratio_recommended = airline_recommended/count_feedback)%>%arrange(-count_feedback)
airline_properties

#I choose the airlines with no too little (>15) feedback number to plot the airline_rating chart in ascending order of ratio_recommended.
airline_properties%>%filter(count_feedback>15)%>%select(airline_rating, ratio_recommended)%>%arrange(ratio_recommended)%>%
ggplot()+
  geom_line(aes(x = ratio_recommended, y = airline_rating))+
  ylab("Airline's rating")+
  xlab("Ratio of recommendation")+
  ggtitle("How recommendation effects overall rating")+
  theme_bw()

```

From this line plot, we have a result that overall_rating is proportional to the recommended rate of customer feedback. As a new airline owner, we need mind on recommeded_ratio. We can change it by getting staff to pay attention to customer feedback
(In this dataset, I thought 'recommended' means the mistakes in customer's feedbacks were fixed or not)






# 2. Let's see how many airlines on the market:
Amount of airlines
```{r}
count(dplyr::distinct(data.frame(c(airline$airline_name, seat$airline_name, lounge$airline_name))))

```
There are 298 airlins on the market


# 3. Here are some top rating of airline, airport, seat and lounge
```{r}
# Top airport
airport_rating = airport%>%select(airport_name, overall_rating, content)%>%na.omit()%>%group_by(airport_name)%>%summarise(airport_rating = mean(overall_rating), count_feedback = n())%>%arrange(-airport_rating)
airport_rating
?top_n
```

```{r}
# Top airline
airline_rating = airline%>%select(airline_name, overall_rating, content)%>%na.omit()%>%group_by(airline_name)%>%summarise(airline_rating = mean(overall_rating), count_feedback_airline = n())%>%arrange(-airline_rating)
airline_rating
```
```{r}
# Top airlines have the best seat
seat_rating = seat%>%select(airline_name, overall_rating, content)%>%na.omit()%>%group_by(airline_name)%>%summarise(seat_rating = mean(overall_rating), count_feedback_seat = n())%>%arrange(-seat_rating)
seat_rating
```
```{r}
# Top airlines have the best lounge
lounge_rating = lounge%>%select(airline_name, overall_rating, content)%>%na.omit()%>%group_by(airline_name)%>%summarise(lounge_rating = mean(overall_rating), count_feedback_lounge = n())%>%arrange(-lounge_rating)
lounge_rating
```



# 4. I created a new dataframe airline_properties that includes variables: airline_name, overall_rating, cabin_flown, recommended, date, author_country
```{r}
lounge = lounge%>%mutate(cabin_flown = lounge_type)
key = c('airline_name', 'overall_rating', 'cabin_flown', 'recommended', 'date', 'author_country')
airline_properties = full_join(full_join(airline, seat, by = key), lounge, by = key)%>%select(airline_name, overall_rating, cabin_flown, recommended, date, author_country)
airline_properties
```
4.1 Rating of customers in each cabin flown
```{r}
airline_properties1 = airline_properties%>%filter(is.na(cabin_flown)==FALSE & cabin_flown != 'Other')
ggplot(data = airline_properties1)+
  geom_boxplot(aes(x = cabin_flown, y = overall_rating, fill = cabin_flown), na.rm = TRUE)+
  ylab("Rating")+
  xlab("Class")+
  theme_bw()+
  ggtitle("Rating of customers in each cabin flown")

```

4.2 Top 10 countries have the most feedback

```{r}
airline_properties%>%group_by(author_country)%>%summarise(count = n(), overall_rating = mean(overall_rating, na.rm = TRUE))%>%arrange(-count)%>%na.omit()%>%head(10)

```


In which months do customers send more feedback? 
```{r}
p = airline_properties%>%mutate(month = lubridate::month(date, label = TRUE))%>%group_by(month)
ggplot(data = p)+
    geom_bar(aes(x = month, fill = factor(recommended, labels = c('Recommended', 'Not recommended'))))+
scale_fill_manual(name = "Recommend feedback", values = c("#DDC488", "#8B814C"))+
theme_bw()
```

In January and July customers send more feedback than all times.




4.3. Draw a graph to describe the correlation between the amount feedback was recommended and the rating of each airline
I created a new dataframe airline_properties2 that was group by airline_name and includes variables: rating, sum_recommended and count_feedback
```{r}
airline_properties2 = airline_properties[1:5]%>%na.omit()%>%group_by(airline_name)%>%summarise(rating = mean(overall_rating), sum_recommended = sum(recommended), count_feedback = n())
ggplot(data = airline_properties2)+
  geom_point(aes(x = rating, y = sum_recommended, size = count_feedback, colour = count_feedback))+
   xlab("Average rating of each airline") +
  ylab("Sum of recommended") +
  ggtitle("Combination the characteristics of each airline")+
  theme_bw()+
  scale_size(name="")+
  scale_color_continuous(name="Amount of feedback")
```



