---
title: "ImportDataInR"
author: "lnguen_1"
date: "12/30/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
```


stringsAsFactors
With stringsAsFactors, you can tell R whether it should convert strings in the flat file to factors.
```{r}
# Import swimming_pools.csv correctly: pools
pools = read.csv('swimming_pools.csv', stringsAsFactors = F)

# Check the structure of pools
str(pools)
```


read.delim
Aside from .csv files, there are also the .txt files which are basically text files. You can import these functions with read.delim(). By default, it sets the sep argument to "\t" (fields in a record are delimited by tabs) and the header argument to TRUE (the first row contains the field names).

```{r}
# Import hotdogs.txt: hotdogs
hotdogs = read.delim("hotdogs.txt", header=F)

# Summarize hotdogs
summary(hotdogs)
```

read.table
If you're dealing with more exotic flat file formats, you'll want to use read.table(). It's the most basic importing function; you can specify tons of different arguments in this function. Unlike read.csv() and read.delim(), the header argument defaults to FALSE and the sep argument is "" by default.

```{r}
# Path to the hotdogs.txt file: path
path <- file.path("hotdogs.txt")

# Import the hotdogs.txt file: hotdogs
hotdogs <- read.table(path, 
                      sep = "\t", 
                      col.names = c("type", "calories", "sodium"))

# Call head() on hotdogs
head(hotdogs)
```

Arguments

```{r}
# Finish the read.delim() call
hotdogs <- read.delim("hotdogs.txt", header = F, col.names = c("type", "calories", "sodium"))

# Select the hot dog with the least calories: lily
lily <- hotdogs[which.min(hotdogs$calories), ]

# Select the observation with the most sodium: tom
tom <- hotdogs[which.max(hotdogs$sodium), ]

# Print lily and tom
lily
tom

```

Column classes
Next to column names, you can also specify the column types or column classes of the resulting data frame. You can do this by setting the colClasses argument to a vector of strings representing classes:
```{r}
# Previous call to import hotdogs.txt
hotdogs <- read.delim("hotdogs.txt", header = FALSE, col.names = c("type", "calories", "sodium"))

# Display structure of hotdogs
str(hotdogs)

# Edit the colClasses argument to import the data correctly: hotdogs2
hotdogs2 <- read.delim("hotdogs.txt", header = FALSE, 
                       col.names = c("type", "calories", "sodium"),
                       colClasses = c("factor", "NULL", "numeric"))


# Display structure of hotdogs2
str(hotdogs2)
```

read_csv
CSV files can be imported with read_csv(). It's a wrapper function around read_delim() that handles all the details for you. For example, it will assume that the first row contains the column names
```{r}
# Load the readr package
library(readr)

# Import potatoes.csv with read_csv(): potatoes
potatoes = read_csv("potatoes.csv")
```

read_tsv
Where you use read_csv() to easily read in CSV files, you use read_tsv() to easily read in TSV files. TSV is short for tab-separated values
```{r}
# readr is already loaded

# Column names
properties <- c("area", "temp", "size", "storage", "method",
                "texture", "flavor", "moistness")

# Import potatoes.txt: potatoes
potatoes = read_tsv("potatoes.txt", col_names = properties)

# Call head() on potatoes
head(potatoes)
```

read_delim
Just as read.table() was the main utils function, read_delim() is the main readr function.

read_delim() takes two mandatory arguments:

file: the file that contains the data
delim: the character that separates the values in the data file
```{r}
# readr is already loaded

# Column names
properties <- c("area", "temp", "size", "storage", "method",
                "texture", "flavor", "moistness")

# Import potatoes.txt using read_delim(): potatoes
potatoes = read_delim("potatoes.txt", delim = "\t", col_names = properties)

# Print out potatoes
potatoes
```

skip and n_max
Through skip and n_max you can control which part of your flat file you're actually importing into R.

skip specifies the number of lines you're ignoring in the flat file before actually starting to import data.
n_max specifies the number of lines you're actually importing.
Say for example you have a CSV file with 20 lines, and set skip = 2 and n_max = 3, you're only reading in lines 3, 4 and 5 of the file.
```{r}
# readr is already loaded

# Column names
properties <- c("area", "temp", "size", "storage", "method",
                "texture", "flavor", "moistness")

# Import 5 observations from potatoes.txt: potatoes_fragment
potatoes_fragment <- read_tsv("potatoes.txt", skip = 6, n_max = 5, col_names = properties)

#skip = start
#n_max = stop
```

col_types
You can also specify which types the columns in your imported data frame should have. You can do this with col_types. If set to NULL, the default, functions from the readr package will try to find the correct types themselves. You can manually set the types with a string, where each character denotes the class of the column: character, double, integer and logical. _ skips the column as a whole.
```{r}
# readr is already loaded

# Column names
properties <- c("area", "temp", "size", "storage", "method",
                "texture", "flavor", "moistness")

# Import all data, but force all columns to be character: potatoes_char
potatoes_char <- read_tsv("potatoes.txt", col_types = "cccccccc", col_names = properties)

# Print out structure of potatoes_char
str(potatoes_char)
```

col_types with collectors
Another way of setting the types of the imported columns is using collectors. Collector functions can be passed in a list() to the col_types argument of read_ functions to tell them how to interpret values in a column.

For a complete list of collector functions, you can take a look at the collector documentation. For this exercise you will need two collector functions:

col_integer(): the column should be interpreted as an integer.
col_factor(levels, ordered = FALSE): the column should be interpreted as a factor with levels.
```{r}
# readr is already loaded

# Import without col_types
hotdogs <- read_tsv("hotdogs.txt", col_names = c("type", "calories", "sodium"))

# Display the summary of hotdogs
summary(hotdogs)

# The collectors you will need to import the data
fac <- col_factor(levels = c("Beef", "Meat", "Poultry"))
int <- col_integer()

# Edit the col_types argument to import the data correctly: hotdogs_factor
hotdogs_factor <- read_tsv("hotdogs.txt",
                           col_names = c("type", "calories", "sodium"),
                           col_types = list(fac, int, int))

# Display the summary of hotdogs_factor
summary(hotdogs_factor)
```



