1. grepl & grep
In their most basic form, regular expressions can be used to see whether a pattern exists inside a character string or a vector of character strings. For this purpose, you can use:

grepl(), which returns TRUE when a pattern is found in the corresponding character string.
grep(), which returns a vector of indices of the character strings that contains the pattern.
Both functions need a pattern and an x argument, where pattern is the regular expression you want to match for, and the x argument is the character vector from which matches should be sought.

In this and the following exercises, you'll be querying and manipulating a character vector of email addresses! The vector emails has already been defined in the editor on the right so you can begin with the instructions straight away!


Use grepl() to generate a vector of logicals that indicates whether these email addressess contain "edu". Print the result to the output.
Do the same thing with grep(), but this time save the resulting indexes in a variable hits.
Use the variable hits to select from the emails vector only the emails that contain "edu".

```{r}
# The emails vector has already been defined for you
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "dalai.lama@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")

# Use grepl() to match for "edu"
grepl(pattern = "edu", x = emails)

# Use grep() to match for "edu", save result to hits
hits = grep(pattern = "edu", x = emails)

# Subset emails using hits
emails[hits]
```

2. grepl & grep (2)
You can use the caret, ^, and the dollar sign, $ to match the content located in the start and end of a string, respectively. This could take us one step closer to a correct pattern for matching only the ".edu" email addresses from our list of emails. But there's more that can be added to make the pattern more robust:

@, because a valid email must contain an at-sign.
.*, which matches any character (.) zero or more times (*). Both the dot and the asterisk are metacharacters. You can use them to match any character between the at-sign and the ".edu" portion of an email address.
\\.edu$, to match the ".edu" part of the email at the end of the string. The \\ part escapes the dot: it tells R that you want to use the . as an actual character.

Use grepl() with the more advanced regular expression to return a logical vector. Simply print the result.
Do a similar thing with grep() to create a vector of indices. Store the result in the variable hits.
Use emails[hits] again to subset the emails vector.

```{r}
# The emails vector has already been defined for you
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "dalai.lama@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")

# Use grepl() to match for .edu addresses more robustly
grepl(pattern = "@.*\\.edu", x = emails)

# Use grep() to match for .edu addresses more robustly, save result to hits
hits = grep(pattern = "@.*\\.edu", x = emails)

# Subset emails using hits
emails[hits]
```

3. sub & gsub
While grep() and grepl() were used to simply check whether a regular expression could be matched with a character vector, sub() and gsub() take it one step further: you can specify a replacement argument. If inside the character vector x, the regular expression pattern is found, the matching element(s) will be replaced with replacement.sub() only replaces the first match, whereas gsub() replaces all matches.

Suppose that emails vector you've been working with is an excerpt of DataCamp's email database. Why not offer the owners of the .edu email addresses a new email address on the datacamp.edu domain? This could be quite a powerful marketing stunt: Online education is taking over traditional learning institutions! Convert your email and be a part of the new generation!


With the advanced regular expression "@.*\\.edu$", use sub() to replace the match with "@datacamp.edu". Since there will only be one match per character string, gsub() is not necessary here. Inspect the resulting output.

```{r}
# The emails vector has already been defined for you
emails <- c("john.doe@ivyleague.edu", "education@world.gov", "global@peace.org",
            "invalid.edu", "quant@bigdatacollege.edu", "cookie.monster@sesame.tv")

# Use sub() to convert the email domains to datacamp.edu
sub(pattern = "@.*\\.edu$", replacement = "@datacamp.edu", x = emails)
```


4. sub & gsub (2)
Regular expressions are a typical concept that you'll learn by doing and by seeing other examples. Before you rack your brains over the regular expression in this exercise, have a look at the new things that will be used:

.*: A usual suspect! It can be read as "any character that is matched zero or more times".
\\s: Match a space. The "s" is normally a character, escaping it (\\) makes it a metacharacter.
[0-9]+: Match the numbers 0 to 9, at least once (+).
([0-9]+): The parentheses are used to make parts of the matching string available to define the replacement. The \\1 in the replacement argument of sub() gets set to the string that is captured by the regular expression [0-9]+.

`awards <- c("Won 1 Oscar.",
  "Won 1 Oscar. Another 9 wins & 24 nominations.",
  "1 win and 2 nominations.",
  "2 wins & 3 nominations.",
  "Nominated for 2 Golden Globes. 1 more win & 2 nominations.",
  "4 wins & 1 nomination.")

sub(".*\\s([0-9]+)\\snomination.*$", "\\1", awards)`

What does this code chunk return? awards is already defined in the workspace so you can start playing in the console straight away.

```{r}
awards <- c("Won 1 Oscar.",
  "Won 1 Oscar. Another 9 wins & 24 nominations.",
  "1 win and 2 nominations.",
  "2 wins & 3 nominations.",
  "Nominated for 2 Golden Globes. 1 more win & 2 nominations.",
  "4 wins & 1 nomination.")

sub(".*\\s([0-9]+)\\snomination.*$", "\\1", awards)
```


