#1. Right here, right now
In R, dates are represented by Date objects, while times are represented by POSIXct objects. Under the hood, however, these dates and times are simple numerical values. Date objects store the number of days since the 1st of January in 1970. POSIXct objects on the other hand, store the number of seconds since the 1st of January in 1970.

The 1st of January in 1970 is the common origin for representing times and dates in a wide range of programming languages. There is no particular reason for this; it is a simple convention. Of course, it's also possible to create dates and times before 1970; the corresponding numerical values are simply negative in this case.


Ask R for the current date, and store the result in a variable today.
To see what today looks like under the hood, call unclass() on it.
Ask R for the current time, and store the result in a variable, now.
To see the numerical value that corresponds to now, call unclass() on it.

```{r}
# Get the current date: today
today = Sys.Date()

# See what today looks like under the hood
unclass(today)

# Get the current time: now
now = Sys.time()

# See what now looks like under the hood
unclass(now)
```


#2. Create and format dates
To create a Date object from a simple character string in R, you can use the as.Date() function. The character string has to obey a format that can be defined using a set of symbols (the examples correspond to 13 January, 1982):

%Y: 4-digit year (1982)
%y: 2-digit year (82)
%m: 2-digit month (01)
%d: 2-digit day of the month (13)
%A: weekday (Wednesday)
%a: abbreviated weekday (Wed)
%B: month (January)
%b: abbreviated month (Jan)
The following R commands will all create the same Date object for the 13th day in January of 1982:

```{r}
as.Date("1982-01-13")
as.Date("Jan-13-82", format = "%b-%d-%y")
as.Date("13 January, 1982", format = "%d %B, %Y")
```


Notice that the first line here did not need a format argument, because by default R matches your character string to the formats "%Y-%m-%d" or "%Y/%m/%d".

In addition to creating dates, you can also convert dates to character strings that use a different date notation. For this, you use the format() function. Try the following lines of code:


```{r}
today <- Sys.Date()
format(Sys.Date(), format = "%d %B, %Y")
format(Sys.Date(), format = "Today is a %A!")
```

In the editor on the right, three character strings representing dates have been created. Convert them to dates using as.Date(), and assign them to date1, date2, and date3 respectively. The code for date1 is already included.
Extract useful information from the dates as character strings using format(). From the first date, select the weekday. From the second date, select the day of the month. From the third date, you should select the abbreviated month and the 4-digit year, separated by a space.


```{r}
# Definition of character strings representing dates
str1 <- "May 23, '96"
str2 <- "2012-03-15"
str3 <- "30/January/2006"

# Convert the strings to dates: date1, date2, date3
date1 <- as.Date(str1, format = "%b %d, '%y")
date2 = as.Date(str2, format = "%Y-%m-%d")
date3 = as.Date(str3, format = "%d/%B/%Y")

# Convert dates to formatted strings
format(date1, "%A")
format(date2, "%d")
format(date3, "%b %Y")
```

#3. Create and format times
Similar to working with dates, you can use as.POSIXct() to convert from a character string to a POSIXct object, and format() to convert from a POSIXct object to a character string. Again, you have a wide variety of symbols:

%H: hours as a decimal number (00-23)
%I: hours as a decimal number (01-12)
%M: minutes as a decimal number
%S: seconds as a decimal number
%T: shorthand notation for the typical format %H:%M:%S
%p: AM/PM indicator
For a full list of conversion symbols, consult the strptime documentation in the console:

?strptime
Again,as.POSIXct() uses a default format to match character strings. In this case, it's %Y-%m-%d %H:%M:%S. In this exercise, abstraction is made of different time zones.



Convert two strings that represent timestamps, str1 and str2, to POSIXct objects called time1 and time2.
Using format(), create a string from time1 containing only the minutes.
From time2, extract the hours and minutes as "hours:minutes AM/PM". Refer to the assignment text above to find the correct conversion symbols!



```{r}
# Definition of character strings representing times
str1 <- "May 23, '96 hours:23 minutes:01 seconds:45"
str2 <- "2012-3-12 14:23:08"

# Convert the strings to POSIXct objects: time1, time2
time1 <- as.POSIXct(str1, format = "%B %d, '%y hours:%H minutes:%M seconds:%S")
time2 = as.POSIXct(str2, format = "%Y-%m-%d %H:%M:%S")

# Convert times to formatted strings
format(time1, "%M")
format(time2, "%I:%M %p")
```

#5. Calculations with Dates
Both `Date` and `POSIXct` R objects are represented by simple numerical values under the hood. This makes calculation with time and date objects very straightforward: R performs the calculations using the underlying numerical values, and then converts the result back to human-readable time information again.

You can increment and decrement `Date` objects, or do actual calculations with them (try it out in the console!):
```{r}
today <- Sys.Date()
today + 1
today - 1

as.Date("2015-03-12") - as.Date("2015-02-27")
```
To control your eating habits, you decided to write down the dates of the last five days that you ate pizza. In the workspace, these dates are defined as five `Date` objects, `day1` to `day5`. The code on the right also contains a vector `pizza` with these 5 `Date` objects.


Calculate the number of days that passed between the last and the first day you ate pizza. Print the result.
Use the function `diff()` on `pizza` to calculate the differences between consecutive pizza days. Store the result in a new variable `day_diff`.
Calculate the average period between two consecutive pizza days. Print the result.


```{r}
day1 = as.Date("2018-10-08")
day2 = as.Date("2018-10-10")
day3 = as.Date("2018-10-15")
day4 = as.Date("2018-10-21")
day5 = as.Date("2018-10-26")


# day1, day2, day3, day4 and day5 are already available in the workspace

# Difference between last and first pizza day
day5 - day1
# Create vector pizza
pizza <- c(day1, day2, day3, day4, day5)

# Create differences between consecutive pizza days: day_diff
day_diff = diff(pizza)
# Average period between two consecutive pizza days
mean(day_diff)
```



#7. Calculations with Times
Calculations using `POSIXct` objects are completely analogous to those using Date objects. Try to experiment with this code to increase or decrease `POSIXct` objects:

```{r}
now <- Sys.time()
now + 3600          # add an hour
now - 3600 * 24     # subtract a day
```

Adding or substracting time objects is also straightforward:

```{r}
birth <- as.POSIXct("1879-03-14 14:37:23")
death <- as.POSIXct("1955-04-18 03:47:12")
einstein <- death - birth
einstein
```

You're developing a website that requires users to log in and out. You want to know what is the total and average amount of time a particular user spends on your website. This user has logged in 5 times and logged out 5 times as well. These times are gathered in the vectors `login` and `logout`, which are already defined in the workspace.


Calculate the difference between the two vectors `logout` and `login`, i.e. the time the user was online in each independent session. Store the result in a variable `time_online`.
Inspect the variable `time_online` by printing it.
Calculate the total time that the user was online. Print the result.
Calculate the average time the user was online. Print the result.

```{r}
login = list("2018-10-12 10:18:04 UTC", "2018-10-17 09:14:18 UTC",
 "2018-10-17 12:21:51 UTC", "2018-10-17 12:37:24 UTC",
 "2018-10-19 21:37:55 UTC")
login = sapply(login, as.POSIXct)
logout = list("2018-10-12 10:56:29 UTC", "2018-10-17 09:14:52 UTC", "2018-10-17 12:35:48 UTC", "2018-10-17 13:17:22 UTC", "2018-10-19 22:08:47 UTC")
logout = sapply(logout, as.POSIXct)



# login and logout are already defined in the workspace
# Calculate the difference between login and logout: time_online
time_online = logout - login
# Inspect the variable time_online
time_online
# Calculate the total time online
sum(time_online)

# Calculate the average time online
mean(time_online)

```

#8. Time is of the essence
The dates when a season begins and ends can vary depending on who you ask. People in Australia will tell you that spring starts on September 1st. The Irish people in the Northern hemisphere will swear that spring starts on February 1st, with the celebration of St. Brigid's Day. Then there's also the difference between astronomical and meteorological seasons: while astronomers are used to equinoxes and solstices, meteorologists divide the year into 4 fixed seasons that are each three months long. (source: www.timeanddate.com)

A vector `astro`, which contains character strings representing the dates on which the 4 astronomical seasons start, has been defined on your workspace. Similarly, a vector `meteo` has already been created for you, with the meteorological beginnings of a season.

Use `as.Date()` to convert the `astro` vector to a vector containing `Date` objects. You will need the `%d`, `%b` and `%Y` symbols to specify the format. Store the resulting vector as `astro_dates`.
Use `as.Date()` to convert the `meteo` vector to a vector with `Date` objects. This time, you will need the `%B`, `%d` and `%y` symbols for the format argument. Store the resulting vector as `meteo_dates`.
With a combination of `max()`, `abs()` and `-`, calculate the maximum absolute difference between the astronomical and the meteorological beginnings of a season, i.e. `astro_dates` and `meteo_dates`. Simply print this maximum difference to the console output.

```{r}

astro = c("20-Mar-2015", "25-Jun-2015", "23-Sep-2015", "22-Dec-2015")
names(astro) = c("spring", "summer", "fall", "winter")
meteo = c("March 1, 15","June 1, 15","September 1, 15", "December 1, 15")
names(meteo) = c("spring", "summer", "fall", "winter")


# Convert astro to vector of Date objects: astro_dates
astro_dates = as.Date(astro, format = "%d-%b-%Y")
# Convert meteo to vector of Date objects: meteo_dates
meteo_dates = as.Date(meteo, format = "%B %d, %y")

# Calculate the maximum absolute difference between astro_dates and meteo_dates
max(abs(meteo_dates - astro_dates))
```

