---
title: "hw4"
author: "lnguen_1"
date: "4/4/2019"
output: 'html_document'
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
```


 
```{r}
library(readr)
library(lubridate)
library(readr)
library(dplyr)
library(stringr)
library(tidytext)
library(wordcloud2)
library(tidyr)
library(ggplot2)
library(knitr)
```
```{r}
movies <- read_csv("~/shared/minor2_2018/data/movies.csv")
ratings <- read_csv("~/shared/minor2_2018/data/ratings.csv")
```

```{r}

##(Data Processing)

```



```{r}
ratings1 = ratings %>% dplyr::group_by(movie_year, movie_id) %>% dplyr::summarise(count_rating = n(),
                                                                     average_rating = mean(rating))

movies = dplyr::full_join(movies, ratings1)
```
```{r}
movies$income = movies$revenue - movies$budget
```
```{r}
# formulate release_date
movies$movie_year = as.character(movies$movie_year)
movies$release_date = str_c(movies$release_date, movies$movie_year)
movies$release_date = dmy(movies$release_date)
```
```{r}
## ???????????????? ??????????????

# source("/principal/courses/minor2_2018/2-tm-net/extract_json.R")

# movies_with_genres = extract_json2(df = movies, col = "genres")

```
```{r}
# extract all json data
# function f_name gets "name"
f_name = function(col){
  x = col
x = str_replace_all(x, '[\\[\\"\\]{}:]', '')
y = str_extract_all(x, 'name [A-z0-9]+( [A-z0-9]+)*')
z = Map(function(i) {return(i%>% str_replace_all('name ', '') %>% str_c(collapse = ', '))}, y)
z = as.character(z)
return(z)
}

# function f_id gets "id"
f_id = function(col){
  x = col
x = str_replace_all(x, '[\\[\\"\\]{}:]', '')
y = str_extract_all(x, '[A-z0-9]+, name')
y = Map(function(i) {return(i%>% str_replace_all('name ', '') %>% str_c(collapse = ', '))}, y)
return(y %>% str_replace_all(', name', ''))
}

movies$genres = f_name(movies$genres)
movies$keywords = f_name(movies$keywords)
movies$production_companies = f_name(movies$production_companies)
movies$production_countries = f_name(movies$production_countries)
movies$spoken_languages = f_name(movies$spoken_languages)

```
```{r}
# remove unnecessary columns
movies = movies %>% select(-spoken_languages, -status, -original_language, -original_title, -homepage)
```
## Preview dataset movies
```{r}
# preview
str(movies)
```





```{r}
##1. Описательная статистика по данным: постановка исследовательского вопроса (не менее 3), ответ на него с помощью графика и интерпретация результатов (3 балла)
```

##Top 10 films with the highest revenue
```{r}
movies$movie_year = as.numeric(movies$movie_year)
knitr::kable(movies %>%select(title, movie_id, revenue, movie_year) %>% arrange(-revenue) %>% head(10))
```





##Top 10 films with the highest budget
```{r}
knitr::kable(movies %>%select(title, movie_id, budget, movie_year) %>% arrange(-budget) %>% head(10))
```





##Top 10 "disaster" movies (lowest income)
```{r}
knitr::kable(movies %>% filter(budget > 15 & revenue > 15) %>% select(title, movie_id, income, movie_year) %>% arrange(income) %>% head(10))
```





##Top 10 most popular movies
```{r}
knitr::kable(movies %>%select(title, movie_id, popularity, movie_year) %>% arrange(-popularity) %>% head(10))
```





##Top 10 most popular genres
```{r}
gen = movies %>%dplyr::select(title, movie_id, genres, movie_year) %>% tidytext::unnest_tokens(genre, genres) %>% dplyr::group_by(genre) %>% dplyr::summarise(count = n()) %>% dplyr::arrange(-count)
knitr::kable(gen %>% head(10))
```

```{r}
gen %>% ggplot()+geom_bar(aes(x = reorder(genre, count), y = count, fill = count), stat = "identity")+coord_flip()+
  xlab("Number of films")+
  ylab("Genre of films")+
  ggtitle("The number of films in each genre")+
  theme_bw()+
  scale_fill_gradient("Count", low = "blue", high = "red")

```





##Top 10 companies produce the most movies
```{r}
knitr::kable(movies %>%select(title, movie_id, production_companies) %>% filter(production_companies != "character(0)") %>% tidytext::unnest_tokens(company, production_companies) %>% dplyr::group_by(company) %>% dplyr::summarise(count = n()) %>% dplyr::arrange(-count) %>% head(10))
```





##Distribution of the number of films produced by month
```{r}
movies$movie_month = lubridate::month(movies$release_date, label = TRUE)
movies %>% dplyr::group_by(movie_month) %>% dplyr::summarise(count = n()) %>% ggplot()+geom_bar(aes(x = movie_month, y = count, fill = count), stat = "identity")+
  xlab("Month")+theme_bw()+
  ylab("Number of films")+
  ggtitle("Distribution of the number of films produced by month")+
  scale_fill_gradient("Count", low = "blue", high = "green")
  

```





##Distribution of the number of films produced by year
```{r}
movies %>% dplyr::group_by(movie_year) %>% dplyr::summarise(count = n()) %>% ggplot()+
  geom_bar(aes(x = movie_year, y = count, fill = count), stat = "identity")+coord_flip()+
  xlab("Number of films")+
  ylab("Year")+
  ggtitle("Distribution of the number of films produced by year")+theme_bw()


```

```{r}
##2. Текстовый анализ описаний к фильмам: связь описаний (частоты, сентимент, темы и т.д.) и какой-либо характеристики фильма (жанр, бюджет и т.д.) -- не менее 2 вопросов (5 баллов)
```

 


```{r}
# Remove punctuation in overview and tagline
library(NLP)
library(tm)
movies$overview = removePunctuation(str_to_lower(movies$overview))
movies$tagline = removePunctuation(str_to_lower(movies$tagline))
```
```{r}
# lemmatization text in overview and tagline
library(textstem)
library(koRpus.lang.en)
library(koRpus)
library(data.table)
movies$overview = lemmatize_strings(movies$overview)
movies$tagline = lemmatize_strings(movies$tagline)

```
```{r}
# list stop words
enstopwords = data.frame(words=stopwords::stopwords("en"), stringsAsFactors=FALSE) 
```


```{r}
# list sentiment of words in english
library(tidytext)
sentiments_bing = tidytext::get_sentiments("bing") %>% dplyr::mutate(words = word) %>% dplyr::select(words, sentiment)
sentiments_nrc = tidytext::get_sentiments("nrc") %>% dplyr::mutate(words = word) %>% dplyr::select(words, sentiment)
sentiments_afinn = tidytext::get_sentiments("afinn") %>% dplyr::mutate(words = word) %>% dplyr::select(words, score)

```

## Annalys keywords

```{r}
# подготовка к сохранению wordcloud как картинки, чтобы можно было вставить несколько в отчет в формате html
library(webshot)
library(htmlwidgets)
```

```{r fig.height=7, fig.width=7}
library(wordcloud2)
```

### Frequence of keywords

####Wordscloud
```{r}
# draw word cloud of keywords
hw_1 = wordcloud2(data = movies %>% unnest_tokens(words, keywords) %>% dplyr::group_by(words) %>% dplyr::summarise(count = n()) %>% dplyr::arrange(-count)%>% anti_join(enstopwords, by = "words") %>% filter(words!="0"))
saveWidget(hw_1,"1.html",selfcontained = F)
webshot::webshot("1.html","1.png", delay = 5)
#webshot::install_phantomjs()

keywords = movies %>% unnest_tokens(words, keywords) %>% dplyr::group_by(words) %>% dplyr::summarise(count = n(), rating_key = mean(average_rating)) %>% dplyr::arrange(-count)%>% anti_join(enstopwords, by = "words") %>% filter(words!="0")
```

####Top 10 words in keywords most popular
```{r}
# top 10 keywords most popular
knitr::kable(keywords %>% head(10), caption = "Frequence of keywords")

```





###Sentiments score of keywords

Keywords with extreme sentiment (point = -5, -4, 4, 5) are rarely used
```{r}
knitr::kable(keywords %>% inner_join(sentiments_afinn) %>% arrange(score) %>% head(10), caption = "Top keywords with the highest score of sentiment")
knitr::kable(keywords %>% inner_join(sentiments_afinn) %>% arrange(-score) %>% head(10), caption = "Top keywords with the lowest score of sentiment")

```







###Distribution of the set sentiment of keywords in each genre
```{r}
key2 = movies %>% tidytext::unnest_tokens(words, keywords) %>% inner_join(sentiments_nrc, by="words") %>% tidytext::unnest_tokens(genre, genres)
conf = as.data.frame.matrix(table(key2$genre, key2$sentiment))
knitr::kable(conf, caption = "Distribution of the set sentiment of keywords in each genre")
```



```{r}
movies %>% unnest_tokens(words, tagline) %>% inner_join(sentiments_nrc, by = "words") %>% unnest_tokens(genre, genres) %>% group_by(genre, sentiment)%>%summarise(count = n()) %>%  ggplot()+geom_histogram(aes(x = genre,y = count, fill = sentiment), stat = "identity")+
  theme(axis.text.x = element_text(angle=60))+
  ggtitle("Distribution of the set sentiment of keywords in each genre")+
  xlab("Genre")+ylab("Count")
```




###Distribution negative/positive keywords in each genres

```{r}
#keywords
key1 = movies %>% tidytext::unnest_tokens(words, keywords) %>% inner_join(sentiments_bing, by="words") %>% tidytext::unnest_tokens(genre, genres)
conf1 = as.data.frame.matrix(table(key1$genre, key1$sentiment))
conf1 = data.frame(row.names(conf1), conf1$negative, conf1$positive)
conf1 = conf1 %>% mutate(genre = row.names.conf1., negative = conf1.negative, positive = conf1.positive) %>% 
  select(genre, negative, positive)
knitr::kable(conf1 %>% arrange(-negative), caption = "Genre drama has the most number of negative keywords")
```





###Now we will calculate sum sentiment in each genre.

```{r}
knitr::kable(movies %>% dplyr::select(title, movie_id, genres, keywords) %>%tidytext::unnest_tokens(words, keywords) %>% dplyr::inner_join(sentiments_afinn, by = "words") %>% unnest_tokens(genre, genres) %>% dplyr::group_by(genre) %>% dplyr::summarise(count = n(), score = sum(score)) %>% arrange(score), caption = "Genre drama has the lowest level of sum sentiment score, then thriller and crime")
```
  
     As you can see, in the most, sentiment score is inversely proportional to number of keywords in each genre. In addition, in most genres, the value of sentiment score is lower than 0, that means film producers tend to use more keywords with negative sentiment than keywords with positive sentiment. Maybe these words are more curiosity to viewers, so they often search for keywords in a more negative sentiment.




## Annalys tagline

###Frequence of words used in tagline

####Wordscloud
```{r}
# draw world cloud for text in tagline
hw_2 = wordcloud2(data = movies %>% unnest_tokens(words, tagline) %>% dplyr::group_by(words) %>% dplyr::summarise(count = n()) %>% arrange(-count) %>% anti_join(enstopwords, by = "words") %>% na.omit())
saveWidget(hw_2,"2.html",selfcontained = F)
webshot::webshot("2.html","2.png", delay = 5)

tagline = movies %>% unnest_tokens(words, tagline) %>% dplyr::group_by(words) %>% dplyr::summarise(count = n(), rating = mean(average_rating)) %>% dplyr::arrange(-rating) %>% anti_join(enstopwords, by = "words") %>% na.omit()
```

####Top 10 words in tagline most popular
```{r}
# top 10 words in tagline most popular
knitr::kable(tagline %>% head(10), caption = "Top 10 words in tagline most popular")
```




####Film producers rarely use words in tagline with extreme sentiments (sentiment with score -5,-4,4,5)


```{r}
knitr::kable(tagline %>% inner_join(sentiments_afinn) %>% arrange(score) %>% head(10), caption = "Arrangement words in tagline by increasing score of sentiment")
knitr::kable(tagline %>% inner_join(sentiments_afinn) %>% arrange(-score) %>% head(10),caption = "Arrangement words in tagline by decreasing score of sentiment")

```



## Analysis overview

### Frequence of words in overviews

####Wordscloud
```{r}
overview = movies %>% tidytext::unnest_tokens(words, overview) %>% dplyr::anti_join(enstopwords)

hw_3 = wordcloud2::wordcloud2(data = overview %>% dplyr::group_by(words) %>% dplyr::summarise(count = n()) %>% filter(count>10))
saveWidget(hw_3,"3.html",selfcontained = F)
webshot::webshot("3.html","3.png", delay = 5)
```

####Top 10 words in overviews most popular
```{r}
knitr::kable(overview %>% dplyr::group_by(words) %>% dplyr::summarise(count = n()) %>% arrange(-count) %>% head(10), caption = "Top 10 words used in overviews most popular")

```





```{r}
genre_score = overview %>% inner_join(sentiments_afinn, by = "words") %>% unnest_tokens(genre, genres) %>% dplyr::group_by(genre) %>% dplyr::summarise(score = sum(score)) %>% arrange(-score)

ggplot(data = genre_score)+ geom_bar(aes(x = reorder(genre, score), y = score, fill = abs(score)), stat = "identity")+
  theme_bw() + scale_fill_gradient("Score")+
  theme(axis.text.x = element_text(angle=60))+
  xlab("Genre") + ylab("Sum score of words\n in all overviews in each genre")+
  ggtitle("Difference of the sum sentiment of words \nin overviews distribution used in each movie genre")
```

    The graph shows genres thriller, crime, horror have lowest level of sum sentiment score of words in overviews. Of couure, in fact, these kind of film include violent, horror contents, so film producer need to use many negative sentimental words to describe the film. In the other hand, level of sum sentiment score in genres romance, family and comedy are high, because they include emotions and homor, need to be described by many positive sentimental words in overviews.





####As in keywords and tagline, film producers also rarely use words in overviews with extreme sentiments (sentiment with score -5,-4,4,5)

```{r}
b = overview %>% group_by(words) %>% summarise(count = n()) %>% inner_join(sentiments_afinn, by ="words")
knitr::kable(b %>% arrange(-score) %>% head(10), caption = "Arrangement of words in overviews by decreasing level of sentiment score")
knitr::kable(b %>% arrange(score) %>% head(10), caption = "Arrangement of words in overviews by decreasing level of sentiment score")

```



